\Large{Adversarial Training against Systematic Uncertainty}

### 2016-10-24 tex/paper.tex
save

To minimize the effects of the nuisance $Z$ in the background events, we train a
classifier using  Algorithm~\ref{alg:adversarial-training} but consider the
adversarial term ${\cal L}_r$ conditioned on $Y=0$ only. Both $f$ and $r$ are
neural networks with 3 hidden layers of 64 nodes and ReLU activations, each
terminated by a single final output node with a sigmoid activation. Training is
performed on a subset of 150000 samples while AMS is evaluated on an independent
test set of 5000000 samples. Results reported below are averages over 5 runs.

>>>>

To minimize the effects of $Z$ in the background events, we train a
classifier using  Algorithm~\ref{alg:adversarial-training} but consider the
adversarial term ${\cal L}_r$ conditioned on $Y=0$ only. Both $f$ and $r$ are
neural networks with 3 hidden layers of 64 nodes and ReLU activations, each
terminated by a single final output node with a sigmoid activation. Training is
performed on a subset of 150000 samples while AMS is evaluated on an independent
test set of 5000000 samples. Results reported below are averages over 5 runs.
